Literature Review: Graphical Models for Articulated Forms, Humans, and Other Objects

### 2012-10-09 newStuff/litReview.tex
reorganized repo, removed superfluous files, cleaned things up a bit.

\begin{abstract}
This is a review of graphical models for representing humans and other objects. Models of both deformable and non-deformable objects allow us, given image and video data, to infer the pose and/or orientation of objects. We aim to either learn the structure and pose of objects, or assume a structure and learn the pose of objects, and incorporate this appearance model into the GPUDDPM detection and tracking scheme.
\end{abstract}

\section{Data}
We take the data to be the same as in the previous paper: frame difference (i.e. foreground, i.e. silhouette) pixel positions, and additional local appearance features

@@

Sigal states, ``we combine techniques from discriminative learning, graphical models, belief propagation, and particle filtering to achieve reliable multi-component object detection and tracking." [p98]

>>>>

\begin{abstract}
This is a review of graphical models for representing humans and other articulated bodies. Models of both deformable and non-deformable objects allow us, given image and video data, to infer the pose and/or orientation of objects. We aim to either learn the structure and pose of objects, or assume a structure and learn the pose of objects, and incorporate this appearance model into the GPUDDPM detection and tracking scheme.
\end{abstract}

\section{Data}
We take our data to be the same as in the previous paper: frame difference (i.e. foreground, i.e. silhouette) pixel positions, and additional local appearance features

@@

Sigal breaks down his framework into five components [p103]
\begin{enumerate} 
\item a graphical model
\item an inference algorithm that provides the ability to infer a state of each node in the graph
\item a local evidence distribution (or image likelihood)
\item a proposal process for some or all nodes in a graphical model
\item a set of spatial and/or temporal constraints corresponding to the edges in a graph
\end{enumerate}
Each object is represented by a undirected graphical model. The model for each object contains a set of four loosely connected regions; for example, a human is represented by head, left arm, right arm, and leg regions. Spatial constraints govern the relative positions of the regions for a given object type, and are modeled with a mixture of Gaussians. Sigal defines a likelihood, which models the probability of image data given one of the regions. Features for the likelihood for each region for a given object are found in a supervised manner, by using a boosted classifier.
